Theories of deliberated choice

### 2023-11-10 simple.tex
Included trivial case

\Cref{def:fals} fills the gap to obtain that $C$ holds iff it is not rejectable.
The property demands that whatever the attitude of individuals, if the attitude is not according to the claim, then it is possible to observe that it is not.
\begin{definition}
  \label{def:fals}
  A claim $C$ is \emph{falsifiable} iff
  $\forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
  %Actually we need to exclude trivial claims with an exists in supplement to forall; so that trivial claims are not falsifiable. Then the property that we seek is trivial-or-falsifiable.
\end{definition}

@@

\Cref{th:holdsiff} shows that falsifiability indeed fills that gap:
falsifiability guarantees that a claim holds if, and only if, it is not rejectable.
\begin{theorem}
  \label{th:holdsiff}
  For any falsifiable claim $C$: $C \ni {\allleadsto}$ iff $\Theta \cap \powerset{\allleadsto} \wsub C^\wsub$.
\end{theorem}
\begin{proof}
  Consider any falsifiable $C$.
  Using the contrapositive of the definition of falsifiability, $\forall {\allleadstog} \in \allleadstos: \nexists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub \implies {\allleadstog} \in C$.
  In particular,
  $\nexists θ \in \Theta \cap \powerset{\allleadsto} \suchthat \theta \notin C^\wsub \implies {\allleadsto} \in C$.
  The reverse implication is proven by \cref{th:ex-post}.
\end{proof}

\begin{definition}
  A claim is \emph{unfalsifiable} iff $\exists {\allleadstog} \notin C \suchthat \Theta \cap \powerset{\allleadstog} \wsub C^\wsub$.
\end{definition}
\begin{definition}
  A non-trivial claim is \emph{strongly unfalsifiable} iff $\Theta \wsub C^\wsub$.
\end{definition}

@@

\section{Technical notes about falsification}
A claim $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$,
equivalently iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.

>>>>

\Cref{def:falsw} fills the gap to obtain that $C$ holds iff it is not rejectable.
The property demands that whatever the attitude of individuals, if the attitude is not according to the claim, then it is possible to observe that it is not.
\begin{definition}
  \label{def:falsw}
  A claim $C$ is \emph{falsifiable or trivial} iff
  $\forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
\end{definition}

@@

\Cref{th:holdsiff} shows that falsifiability indeed fills that gap:
falsifiability guarantees that a claim holds if, and only if, it is not rejectable.
\begin{theorem}
  \label{th:holdsiff}
  For any falsifiable or trivial claim $C$: $C \ni {\allleadsto}$ iff $\Theta \cap \powerset{\allleadsto} \wsub C^\wsub$.
\end{theorem}
\begin{proof}
  Consider any falsifiable $C$.
  Using the contrapositive of \cref{def:fals}, $\forall {\allleadstog} \in \allleadstos: \nexists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub \implies {\allleadstog} \in C$.
  In particular,
  $\nexists θ \in \Theta \cap \powerset{\allleadsto} \suchthat \theta \notin C^\wsub \implies {\allleadsto} \in C$.
  The reverse implication is proven by \cref{th:ex-post}.
\end{proof}

\begin{definition}
  A claim is \emph{strongly unfalsifiable} iff 
  $\Theta \wsub C^\wsub$.
\end{definition}

@@

\section{Technical notes about falsification}
\begin{definition}
  \label{def:fals}
  A claim $C$ is \emph{falsifiable} iff
  $C \neq {\allleadstos} \land
  \forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
\end{definition}
\begin{definition}
  A claim is \emph{unfalsifiable} iff 
  $C = {\allleadstos} \lor
  \exists {\allleadstog} \notin C \suchthat \Theta \cap \powerset{\allleadstog} \wsub C^\wsub$.
\end{definition}

A claim $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$,
equivalently iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
(To be corrected for the trivial claims.)
